### 2016-03-12 experiments.tex
Alex ready to ship

Over all mutants, and all pairs of test cases repaired by the same mutant (so the same pair may count many times, if many mutants repair both test cases), the probability of being due to the same fault was 42.77\%, and the probability of being due to the same fault if two test cases disagreed on a repair (the mutant repaired one test case but not the other) was only 20.33\%.  The baseline rate for same-fault for test pairs was 33.64\%.  Just knowing that two test cases have \emph{one} shared repairing mutant makes it 1.27x more likely that they are the same fault, and knowing they differ for one mutants makes it 0.6 times as likely they are due to the same fault.  Matching non-repair provides very weak evidence:  only a 34.14\% chance of matching fault.

@@

Results are reported as absolute ranks, rather than more sophisticated \cite{MUSE} localization evaluations because our localizations do not assign suspiciousness scores, only rankings, and in accord with the proposal of Parnin and Orso that only localizations ranking a fault in the top few statements may be useful to users \cite{AutoHelp}.  We expect users to examine coverage changes and mutants.  Blind, unaided pointers to portions of compiler code without more semantic information about why the statement is suspicious seems unlikely to work well, based on our experience with complex compiler faults, and the results of Parnin and Orso \cite{AutoHelp}.

@@

Table \ref{gcctable} shows localization results for GCC 4.3.0 wrong code faults.  For the same reasons as with SpiderMonkey, only some faults were deemed to have a strong enough ground truth patch for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but this was its only useful localization.  MUSEUM provided three useful localizations, but no very high quality localizations.  Only {\bf Repair} performed extremely welwith useful localizations for 5 faults, and localizations with the fault in the top-5 statements for 4 of these.

@@

In one sense, the discovery curve improvements here are practically useful, but not spectacular.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very best curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank competing curves, so this is not a practical approach to fuzzer taming.  The best methods for different subjects in previous work varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, previous work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential properties.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.

>>>>

Over all mutants, and all pairs of test cases repaired by the same mutant (so the same pair may count many times, if many mutants repair both test cases), the probability of being due to the same fault was 42.77\%, and the probability of being due to the same fault if two test cases disagreed on a repair (the mutant repaired one test case but not the other) was only 20.33\%.  The baseline rate for same-fault for test pairs was 33.64\%.  Just knowing that two test cases have \emph{one} shared repairing mutant makes it 1.27x more likely that they are the same fault, and knowing they differ for one mutant makes it 0.6 times as likely they are due to the same fault.  Matching non-repair provides very weak evidence:  only a 34.14\% chance of matching fault.

@@

Results are reported as absolute ranks, rather than more sophisticated \cite{MUSE} localization evaluations because our localizations do not assign suspiciousness scores, only rankings, and in accord with the proposal of Parnin and Orso that only localizations ranking a fault in the top few statements may be useful to users \cite{AutoHelp}.  We expect users to examine coverage changes and mutants.  Blind, unaided pointers to portions of compiler code without more semantic information about why the statement is suspicious seem unlikely to work well, based on our experience with complex compiler faults, and the results of Parnin and Orso \cite{AutoHelp}.

@@

Table \ref{gcctable} shows localization results for GCC 4.3.0 wrong code faults.  For the same reasons as with SpiderMonkey, only some faults were deemed to have a strong enough ground truth patch for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 30) localizations.  {\bf Coverage} produced one very good localization, and was the only method to localize that fault at all, but this was one of only two useful localizations.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed extremely well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

@@

In one sense, the discovery curve improvements here are practically useful, but not spectacular.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very best curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank curves, so PLDI 13 does not really give a practical approach to distance metric selection.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, previous work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential properties.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.
